---
title: "Using Your Own Data Guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NetPhorce}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This guide will help guide you to savely load your own data.

## 1. Correctly Loading MaxQuant Data
The original column names from MaxQuant contains spaces, which must be parsed as space for `NetPhorce::confirmIntensityColumns()` function to run, here we demonstrate one of the ways to correctly load the MaxQuant data to R environment via `read_delim` from tidyverse.

```{r, eval=FALSE}
library(tidyverse)
maxquantData = read_delim("<Path_to_Your_MaxQuant_File>", delim = "\t")
```

Once the data is loaded, please make sure you check on of the intensity column, i.e. "Intensity HT_0min_A___1", and make sure there is a space between "Intensity" and the TIME/REP/CON string. You can use the following script demo to check
```{r, eval=FALSE}
knownColumnName = "Intensity HT_0min_A___1"
knownColumnName %in% colnames(maxquantData)
```

The output from the knownColumnName %in% colnames(maxquantData) need to return `TRUE`.






































