---
title: "Shiny Plot Object to R"
author: "Kuncheng Song"
date: "3/26/2022"
output: html_document
vignette: >
  %\VignetteIndexEntry{Shiny Plot Object to R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(NetPhorce)
library(curl)
```


## Introduction
The plot generation can be split into three categories: 

1. Multiple Plots: Most of the plots generated from the NetPhorce pipeline is part of this cateogry. 
2. Regulation Plot: Contains regulation data. 
3. Network Plot: Interactive Network Plot data contains the network results. 

## 1.0 Multiple Plots
The following plots using the same NetPhorce object:

+ "DistributionPlot"
+ "Boxplot", which is the Histogram/Boxplot 
+ "PCA_Normalized_Plot"
+ "PCA_Unnormalized_Plot"
+ "SignificantPeptidesHeatmap"
+ "AbsencePresencePeptidesHeatmap"
+ "IndividualPeptide"
+ "MultiplePeptides_Top"
+ "MultiplePeptides_Bottom"

All of these plot using the same dataset, please follow the guides from the Plot Demonstration under 'Articles' for detailed plotting guides, it should begin with the following commands:
```{r}
githubURL <- ("https://github.com/ksong4/NetPhorceTutorialData/raw/main/RPackageDemo/PCA_Normalized_Plot.RDS")
netPhorceData_V1  <- readRDS(url(githubURL, method="libcurl"))
netPhorceData_V1 = convertShinyToR(netPhorceData_V1)
```

### 1.1 Plot Example
```{r}
plotDistribution(netPhorceData = netPhorceData_V1,
                 condition = "Col0",
                 plotly = FALSE)
uniqueIDs <- 
  findUniqueIDs(netPhorceData = netPhorceData_V1,
                uniqueIDList = c(
                  # Significant Set Examples: 
                  "AT1G13030.1", "AT1G13360.3", "AT1G42550.1", 
                  # Unique/Abscence Set Examples 
                  "AT1G17280.9", "AT1G22310.2", "AT1G23890.2" 
                ),
                verbose = TRUE)
plotUniqueIDsHeatmaps(netPhorceData = netPhorceData_V1,
                      foundUniqueIDs = uniqueIDs,
                      heatmapType = "Significant",
                      minQVal = 0.05,
                      plotly = TRUE)
```

### 1.2 Plot Source Data
If you wish to replot to edit the colors, fills and design, please view our source code for each of the plotting methods, here is the original data we used to generate the plot, please aware some degree of data manimpuation are done to transform the data. Universaly, we use the study design from "netPhorceData@Design$ConDesign", and the basic data are stored in "netPhorceData@data.filtered". 

## 2.0 Regulation Plot
```{r}
githubURL <- ("https://github.com/ksong4/NetPhorceTutorialData/raw/main/RPackageDemo/RegulationPlot.RDS")
netPhorceData_V2  <- readRDS(url(githubURL, method="libcurl"))
netPhorceData_V2 = convertShinyToR(netPhorceData_V2)
```

### 2.1 Regulation Plot
```{r}
plotRegulation(netPhorceData_V2, condition = "Col0")
```

## 3.0 Network Plot
```{r}
githubURL <- ("https://github.com/ksong4/NetPhorceTutorialData/raw/main/RPackageDemo/VisNetworkPlot_Left.RDS")
netPhorceData_V3  <- readRDS(url(githubURL, method="libcurl"))
netPhorceData_V3 = convertShinyToR(netPhorceData_V3)
```

### 3.1 Plot Network
```{r}
plotNetPhorce(netPhorceData_V3, condition = "Col0")
```













